\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-11 paper/experiments.tex
paper: added data section for fcc dataset

\section{Experiments}
\todo{we of course need to rewrite this whole section}
To evaluate the performance of our system, we generate plans for queries on two data sets: the American Community Survey and a synthetic dataset.
\subsection{Data sets} \label{subsec:datasets}
\subsubsection{Center for Disease Control: Surveys}
For our first set of experiments, we use survey data collected by the 
Center for Disease Control (CDC) in the United States. In particular, we
experiment on a set of tables collected as part of the National
Health and Nutrition Examination Survey (NHANES), a series of studies
conducted by the CDC on a national sample of several thousand individuals\cite{nhanes}.
The data consists on survey responses, physical examinations, and laboratory
results, amongst others. Our dataset corresponds to the 2013-2014 NHANES
and is available for direct download on the CDC's organization site on 
kaggle.com, a popular data science website.

@@

\begin{table}
    \centering
    \begin{subtable}{0.5\textwidth}
        \centering
       \input{tables/cdc_demo}
        \caption{Demographics}
    \end{subtable}
    \begin{subtable}{0.5\textwidth}
        \centering
        \input{tables/cdc_labs}
        \caption{Laboratory Results}
    \end{subtable}
       \begin{subtable}{0.5\textwidth}
        \centering
        \input{tables/cdc_exams}
        \caption{Physical Results}
    \end{subtable}
    \caption{Missing values in CDC NHANES 2013-2014 data}
\end{table}

@@

\subsubsection{Some Other TBD dataset}
\todo{write data description for this}

>>>>

\section{Experiments}
\todo{we of course need to rewrite this whole section}
To evaluate the performance of our system, we generate plans for queries
for two separate survey-based data sets, showing that our system
is ideal for early dataset exploration.

\subsection{Data sets} \label{subsec:datasets}
\subsubsection{Center for Disease Control: Surveys}
For our first set of experiments, we use survey data collected by the 
Center for Disease Control (CDC) in the United States. In particular, we
experiment on a set of tables collected as part of the National
Health and Nutrition Examination Survey (NHANES), a series of studies
conducted by the CDC on a national sample of several thousand individuals\cite{cdc-data}.
The data consists on survey responses, physical examinations, and laboratory
results, amongst others. Our dataset corresponds to the 2013-2014 NHANES
and is available for direct download on the CDC's organization site on 
kaggle.com, a popular data science website.

@@

\begin{table}
    \centering
    \begin{subtable}{0.5\textwidth}
        \centering
       \input{tables/cdc_demo}
        \caption{Demographics}
    \end{subtable}
    \begin{subtable}{0.5\textwidth}
        \centering
        \input{tables/cdc_labs}
        \caption{Laboratory Results}
    \end{subtable}
       \begin{subtable}{0.5\textwidth}
        \centering
        \input{tables/cdc_exams}
        \caption{Physical Results}
    \end{subtable}
    \caption{Missing values in CDC NHANES 2013-2014 data}
    \label{table:nhanes-description} 
\end{table}

@@

\subsubsection{freeCodeCamp: 2016 New Coder Survey}
For our second set of experiments, we chose to use data collected
by freeCodeCamp as a part of a survey of new software developers
(both professional and amateur). freeCodeCamp is an open-source
community that intends to help users learn how to program. In addition,
to providing training material for users, it also pairs users with
nonprofits to develop software solutions. Their \textit{2016 New Coder Survey} consists of responses by over 15,000 people to 48 different
questions. The survey targeted users who were in one way or another
related to coding organizations.

For our purposes, we use a version of the data that has been 
pre-processed, but where plenty of missing values remain. It is
worth noting that given the table design (where many attributes
are related), many of these missing values are to be
expected. The dataset we started with had 15,620 rows and 113
columns. We chose 17 attributes, which are outlined in Table~\ref{table:fcc-description}, along with the percentage of missing values.

\begin{table}
   \centering
    \input{tables/fcc}
    \caption{Missing values in FCC Survey Data}
   \label{table:fcc-description} 
\end{table}
